Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
added W1 large-scale map figure

Figures \ref{fig:w2_large} and 5 show large-scale renderings of our full-depth 
coadds over the north and south Galactic caps respectively. It is 
apparent that the Moon contamination has been completely eliminated in
W1 and dramatically reduced in W2. It is possible that simply folding in 
additional NEOWISER W2 frames from forthcoming data releases will diminish the 
remaining Moon imprint to such an extent that no additional processing 
modifications will be required to address this issue.

@@

@@

\begin{figure}[ht]
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=3.0in}
  \caption{\label{fig:image_noise} Illustration of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure}

>>>>

Figures \ref{fig:w2_large} and \ref{fig:w1_large} show large-scale renderings 
of our full-depth coadds over the north and south Galactic caps respectively. 
It is apparent that the Moon contamination has been completely eliminated in
W1 and dramatically reduced in W2. It is possible that simply folding in 
additional NEOWISER W2 frames from forthcoming data releases will diminish the 
remaining Moon imprint to such an extent that no additional processing 
modifications will be required to address this issue.

@@

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w1_large_scale.eps, width=7.0in}
  \caption{\label{fig:w1_large} A sub-section of the region shown in Figure
           \ref{fig:w2_large}. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. Scattered moonlight has effectively
           been completely eliminated in W1.}
 \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=6.0in}
  \caption{\label{fig:image_noise} Example of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure*}
